Methods for Large Scale Learning to Rank

### 2014-02-25 report/Chapters/Introduction.tex
versteviging introduciton

%********************************************************************
% Appendix
%*******************************************************
% If problems with the headers: get headings in appendix etc. right
%\markboth{\spacedlowsmallcaps{Appendix}}{\spacedlowsmallcaps{Appendix}}
\chapter{Motivation and Problem Statement}
Ranking is a core problem in the field of information retrieval. The ranking task in information retrieval entails the ranking of candidate documents according to their relevance for a query. Research in the field of ranking models has for a long time been based on manually designed ranking functions and has been an active area of research since Luhn\cite{Luhn1957} was the first to propose a model that assigned relevance scores to documents given a query back in 1957. The increasing amounts of potential training data have recently made it possible to leverage machine learning methods to obtain more effective models. Learning-to-Rank is the relatively new research area covering the use of machine learning models for the ranking task.\\

>>>>

%********************************************************************
% Appendix
%*******************************************************
% If problems with the headers: get headings in appendix etc. right
%\markboth{\spacedlowsmallcaps{Appendix}}{\spacedlowsmallcaps{Appendix}}
\chapter{Motivation and Problem Statement}
Ranking is a core problem in the field of information retrieval. The ranking task in information retrieval entails the ranking of candidate documents according to their relevance for a query. Ranking is useful in many other application domains as well, amongst others in drug discovery, to determine the order of maintenance operations\cite{Rudin2009}. Learning-to-Rank has also been argued to be a more fitting approach to recommender systems than rating prediction\cite{Adomavicius2005,McNee2006}.\\

Research in the field of ranking models has for a long time been based on manually designed ranking functions and has been an active area of research since Luhn\cite{Luhn1957} was the first to propose a model that assigned relevance scores to documents given a query back in 1957. The increasing amounts of potential training data have recently made it possible to leverage machine learning methods to obtain more effective models. Learning-to-Rank is the relatively new research area covering the use of machine learning models for the ranking task.\\
